Tutorial 3b

### 2024-12-16 Tutorial_1b.Rmd
update Rmd & html files

---
title: "Tutorial_1b"
author: "Sven Panis"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    theme: united
editor_options: 
  chunk_output_type: console
---

>>>>

---
title: "Tutorial 1b"
author: "Sven Panis"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    theme: united
editor_options: 
  chunk_output_type: console
---

### 2024-12-16 Tutorial_2a.Rmd
update Rmd & html files

---
title: "Tutorial_2a"
author: "Sven Panis"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    theme: united
editor_options: 
  chunk_output_type: console
---

@@

For example, the coefficients for x vary from -0.13 to 0.6, and we might specify N(.3,.25) as a prior distribution, Those for x-squared vary from -0.11 to 0.12, and we might specify N(0,.06) as a prior distribution.

@@

Finally, perform a ppc for the selected prior distributions for M0c (see lines 369-374), and increase the standard deviation for the normal prior for class "sd" somewhat.

>>>>

---
title: "Tutorial 2a"
author: "Sven Panis"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    theme: united
editor_options: 
  chunk_output_type: console
---

@@

For example, the coefficients for x vary from -0.13 to 0.6, and we might specify N(.3,.25) as a prior distribution. Those for x-squared vary from -0.11 to 0.12, and we might specify N(0,.06) as a prior distribution.

@@

Finally, perform a ppc for the selected prior distributions for M0c (see lines 220-224), and increase the standard deviation for the normal prior for class "sd" somewhat.

### 2024-12-16 Tutorial_2b.Rmd
update Rmd & html files

---
title: "Tutorial_2b"
author: "sven panis"
date: "2024-10-18"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    theme: united
editor_options: 
  chunk_output_type: console
---

@@

As we expect conditional accuracies ranging between (and including) 0 and 1, we use a flat prior on the logit scale for our intercepts (see section E in the supplemental material).

@@

```{r save-epred-grand, eval=F}
ggsave("Tutorial_2_Bayesian/figures/M1i_ca_pred_grand.png", width = 10, height = 8, dpi = 800)
```

@@

```{r save-epred-pid, eval=F}
ggsave("Tutorial_2_Bayesian/figures/M1i_ca_pred_pid.png", width = 10, height = 8, dpi = 800)
```

@@

```{r save-grand-AMEs, eval=F}
ggsave("Tutorial_2_Bayesian/figures/M1i_ca_grand_AME.png", width = 10, height = 8, dpi = 800)
```

@@

```{r save-pid-AMEs, eval=F}
ggsave("Tutorial_2_Bayesian/figures/M1i_ca_pid_AMEs.png", width = 10, height = 8, dpi = 800)
```

>>>>

---
title: "Tutorial 2b"
author: "sven panis"
date: "2024-10-18"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    theme: united
editor_options: 
  chunk_output_type: console
---

@@

As we expect conditional accuracies ranging between (and including) 0 and 1, we use a flat prior on the logit scale for our intercepts (see Supplementary Figure 2 in section E of the Supplemental Material).

@@

@@

@@

@@

### 2024-12-16 Tutorial_3a.Rmd
update 3a 3b 4.Rmd
update Rmd & html files

---
title: "Tutorial_3a"
author: "Sven Panis"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    theme: united
editor_options: 
  chunk_output_type: console
---

@@

```{r load-pkg, results='hide'}
pkg <- c("tidyverse", "RColorBrewer", "patchwork", "lme4", "nlme", "broom.mixed")

@@

```{r inspect-M1i-f}
load("Tutorial_3_Frequentist/model_M1i_f.RData")
summary(model_M1i_f)
```

>>>>

---
title: "Tutorial 3a"
author: "Sven Panis"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    theme: united
editor_options: 
  chunk_output_type: console
---

@@

```{r load-pkg, results='hide'}
pkg <- c("tidyverse", "RColorBrewer", "patchwork", "lme4", "nlme", "broom.mixed", "rstan")

@@

```{r inspect-M1i-f}
load("Tutorial_3_Frequentist/model_M1i_f.RData")
fixef(model_M1i_f)
```

### 2024-12-16 Tutorial_3b.Rmd
update 3a 3b 4.Rmd
update Rmd & html files

---
title: "Tutorial_3b"
author: "sven panis"
date: "2024-10-18"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    theme: united
editor_options: 
  chunk_output_type: console
---

@@

```{r effects-M1i-ca-f}
load("Tutorial_3_Frequentist/model_M1i_ca_f.RData")
summary(model_M1i_ca_f)
```

>>>>

---
title: "Tutorial 3b"
author: "sven panis"
date: "2024-10-18"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    theme: united
editor_options: 
  chunk_output_type: console
---

@@

```{r effects-M1i-ca-f}
load("Tutorial_3_Frequentist/model_M1i_ca_f.RData")
fixef(model_M1i_ca_f)
```
